On the presentation of orthogonal groups over polynomial rings

### 2019-08-05 dl-paper.tex
Proving 5.30

%If we denote the kernel of the natural transformation $\mu$ from the definition of $\St(\Phi, R, I)$ by $C(\Phi, R, I)$ we obtain a natural exact sequence:
%\begin{equation} \label{relSteinberg-def}  \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r]^{j} & \St(\Phi, R, I) \ar[r]^{\mu} & \St(\Phi, R) \ar[r]^{\pi} & \St(\Phi, R/I) \ar[r] & 1.} \end{equation}
%The group $C(\Phi, R, I)$ is trivial when $I$ is a splitting ideal of $R$, i.\,e. when the canonical map $R \to R/I$ splits, see \cite[Lemma~8]{S15}.

@@

\item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
\item\label{Z5} If $\alpha+\beta\in\Phi$, then holds:
\begin{multline} \nonumber z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s)\cdot x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
  x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta)\text{ where $\epsilon = N_{\alpha,\beta}$.}\end{multline}
\end{enumerate} \end{lemma}
\begin{proof}
The first four assertions are contained in~\cite[Lemma~9]{S15}, so it remains to verify the last assertion.
Direct computation shows that
\begin{multline} \nonumber
  z_{\alpha+\beta}(s\eta, \xi) = [x_\alpha(\epsilon s)^{x_{-\alpha-\beta}(\xi)}, x_\beta(\eta)^{x_{-\alpha-\beta}(\xi)}] =
  [x_\alpha(\epsilon s) x_{-\beta}(-s\xi), x_{\beta}(\eta) x_{-\alpha}(\epsilon \xi\eta)] = \\ 
  = x_\alpha(\epsilon s) \cdot x_{-\beta}(-s\xi) \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta)^{x_{\beta}(-\eta)} \cdot z_{-\beta}(s\xi, -\eta)^{x_{-\alpha}(-\epsilon \xi\eta)},
\end{multline} 
and the required assertion follows from~\eqref{Z2}.
\end{proof}

@@

Finally, the final relation can be verified by the following direct computation, which involves identity $[x, yz]^y = [y^{-1}, x] \cdot [x, z]$ and \eqref{HW-variant} with both sides of the equation inverted:
\begin{multline} \nonumber [x_{\alpha+\beta}(s), x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s), [x_{-\alpha}(-\epsilon t), x_{-\beta}(\xi)]] = \\ 
= \left([[ x_{\alpha+\beta}(-s), x_{-\alpha}(\epsilon t)], x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s)} \cdot  [[ x_{-\beta}(-\xi), x_{\alpha+\beta}(s)], x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)}\right)^{x_{-\alpha}(\epsilon t)} = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)x_{-\alpha}(\epsilon t)}  = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t) x_{-\alpha-\beta}(t\xi)] ^ {x_{-\alpha}(\epsilon t)} = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [x_{-\alpha}(-\epsilon t), x_{\alpha}(\epsilon s\xi)] \cdot [x_{\alpha}(\epsilon s\xi), x_{-\alpha-\beta}(t\xi)] = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2). \qedhere
\end{multline}

\begin{comment}
\begin{multline} 
 [x_\alpha(m), x_{-\alpha}(X\xi)] = [x_\alpha(m), [x_{-\alpha-\beta}(N_{-\alpha-\beta, \beta} X), x_{\beta}(\xi)]] = \\ = \left([[ x_\alpha(m), x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)], x_{\beta}(\xi)] ^ {x_\alpha(-m)} \cdot  [[ x_{\beta}(-\xi), x_\alpha(m)], x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)] ^ {x_{\beta}(-\xi)}\right)^{x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)} = \\ = \left([x_{-\beta}(-N_{-\alpha-\beta,\beta}N_{\alpha,-\alpha-\beta}mX), x_{\beta}(\xi)] ^ {x_\alpha(-m)} \cdot  [ x_{\alpha + \beta}(-N_{\beta, \alpha}m\xi), x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)] ^ {x_{\beta}(-\xi)}\right)^{x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)} =
\end{multline}
\end{comment}
\end{proof}

@@

\section{Proof of the second part of the injectivity theorem}

\subsection{Presentation of Steinberg groups by homogeneous generators}
\label{sec:presentation}
%Throughout this section $\Phi$ is a root system of type $\rA_{\geq 4}$, $\rD_{\geq 5}$, $\rE_{6,7,8}$ and $A$ is a local ring with maximal ideal $M$.
Let $I\trianglelefteq A$ be an ideal of a commutative ring $A$.
We consider $A[t, t\inv]$ as a $\mathbb{Z}$-graded ring in which $t$ has degree $1$.
We denote by $B = B(A, I)$ the subring $A[t] + I[t\inv] \subseteq A[t, t\inv]$ with the induced grading.
As an $A$-module $B$ decomposes as $\oplus_{d\in\mathbb Z}B_d$ where $B_d=I \cdot t^d$ for $d<0$, and $B_d=A \cdot t^d$ for $d\geq0$. Obviously, $B = A[t]$ in the case $I=0$ and $B = A[t, t\inv]$ in the case $I=A$.

@@

Finally, suppose $g$ has type $5$.
Substituting in~\eqref{Z5} of~\cref{Zrels} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$ and expressing $z_\alpha(f, mX)$ through other terms we obtain that
\begin{multline} \label{eq:zalpha} z_\alpha(f, mX) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-mX^2 f) \cdot x_{-\beta}(mf) \cdot x_\alpha(f) \cdot \\ 
 \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon m) \cdot z_{-\beta}(-mf, -X) \cdot x_{-\alpha-\beta}(-\epsilon m^2X f) \cdot x_{-\alpha}(-m^2X^2 f), \end{multline}
and the latter expression is a product of generators of type 1, 1, 2, 5, 1, 2, 1, 4. \end{proof}

@@

Let us verify the assertion for the generator of type 4.
Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$. 
Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \beta$ into~\eqref{Z5} of~\cref{Zrels} we obtain that
\begin{multline} \label{eq:Zconj3} z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
 \cdot z_{-\alpha-\beta}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\beta}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{-\beta}(a f, -X), \end{multline}
where $\epsilon = N_{-\alpha-\beta,\beta}$. 
Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 4, 1, 1, 5, 2. \end{proof}

@@

\subsection{Construction of a model for $\St(\Phi, A[X\inv] + M[X])$}
Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise.
Let $A$ be a local ring with maximal ideal $M$.
As in~\cref{firstPart} we denote by $B$ the ring $A[X\inv] + M[X]$ considered as a graded subring of $A[X, X\inv]$. The notation of the present subsection is consistent with~\cref{sec:presentation} if we set $t = X\inv$, $I = M$.

For shortness we denote the subgroup $\overline{\St}(\Phi, A, M)$ by $G_M^0$.
Notice that $G_M^0$ can be considered as a subgroup of $\St(\Phi, A[X, X\inv])$.
\[ \xymatrix{ G_M^0 \ar@{^{(}->}[r]^{i_+} \ar@{^{(}->}[d]^{i_-} & \overline{\St}(\Phi, A[X], M[X]) \ar^{j_+^M}[d] \ar@{^{(}->}[r] & \St(\Phi, A[X]) \ar[dl]^{j_+} \\
              \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, A[X, X\inv]) &  } \] 
We denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. 
Denote by $V$ the subset of \[\St(\Phi, A[X, X\inv]) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times\] consisting of those triples $(g, h, u)$ for which
\[p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}\] belongs to $\overline{G}_M^{\geq 0}$.

@@

 Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on a choice of the representative.
 Let $(g, h_1, u) \sim (g, h_2, u)$ be elements of the same orbit for which both $p(g, h_1, u)$ and $p(g, h_2, u)$ belong to $P_\alpha(*)$.
 By definition, $h_1^{-1} h_2 = i_-(h_0)$, for some $h_0 \in G^0_M$, moreover, 
  $p(g, h_1, u)^{-1} \cdot p(g, h_2, u) = j_- i_-(h_0) = j_+ i_+(h_0) \in P_\alpha(*)$.
 By~\cref{Pstar-char} there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $g_0 := ev^*_{X=0}(g_1) \in Z_\alpha(A, M)$ and $j_+(g_1) = j_+ i_+ (h_0)$.
 From the last equality and the injectivity of the map $G(\Phi, A[X]) \to G(\Phi, A[X, X^{-1}])$ we obtain that
 the projections of $g_0$, $g_1$ and $h_0$ in $G(\Phi, A[X, X^{-1}])$ are equal, which shows that $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$. 
 It follows from Stein's theorem that the latter subgroup is generated by relative Steinberg symbols $\{ a, 1 + m \}$ and therefore is contained in $Z_\alpha(A, M)$ by~\cref{Z-DS}. Thus, we have obtained that $h_0 \in Z_\alpha(A, M)$ and hence that $i_-(h_0)$ is centralized by $X_\alpha(A[X^{-1}])$, which allows us to conclude that
 \begin{multline} \nonumber
  t_\alpha(aX^{-1})(g, h_1, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) \sim \\
  \sim \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 i_-(h_0) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) = t_\alpha(aX^{-1})(g, h_2, u). \qedhere
 \end{multline} \end{proof}

@@

%The following proposition is a direct generalization of~\cite[Proposition~4.3]{Tu83}.

@@

\begin{lemma} \label{R2_0_1} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations $\mathrm{R2}_{0,1}$. \end{lemma}
\begin{proof} 
\begin{comment}
Suppose $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
Set $h' := x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-bX^{-1}\left(1 + \tfrac{bm}{1+am}\right)^{-1}\right) =
  x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
The assertion for $\text{R1}_1$ is obtained via~\cref{SR:additivity}:
\begin{multline} \nonumber T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
 = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline} 
\end{comment}
Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$.
As before, we may assume $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m, m' \in M$.
Now for $a, b \in A$ set $\epsilon = N_{\alpha, \beta},$ $c = 1 - \epsilon abm'$.
Applying~\cref{SR:obtuse} to the pair of roots $\alpha, \alpha+\beta$ we obtain that 
\begin{multline} \nonumber
[T_\beta(b), T_\alpha(aX^{-1})] \left(g, [h], u \right) = \\
 %= T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1}) \cdot g, \left[h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right)\right], u (1 - am) \right) = \\
 = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1}) g,\ [h'],\ u (1 - am) \right) = \\
 = \left([x_\beta(b), x_\alpha(aX^{-1})]\cdot g,\ [h''],\ u c\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u),\end{multline} 
 where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc)$  
  and the last equality is obtained as follows:
 \begin{multline} \nonumber
 h'' = h' \cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \sim \\ \sim  h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) = \\
 = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \sim
 h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right). \qedhere
\end{multline}
\end{proof}

@@

This action satisfies the following additional property. If $v = (g, [h], u) \in \overline{V}$ is such that $\overline{p}(v) = \overline{1} = G_M^0$ then for any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_-(h_1) \cdot v = (h_1 \cdot g, [h \cdot h_1^{-1}], u)$ and, moreover, $\overline{p}(j_-(h_1) \cdot v) = \overline{1}$.
\end{prop}
\begin{proof}
  By~\cref{superfluous-relations} and Lemmas~\ref{R3_leq0_1}--\ref{R2_0_1} the action of $\St^{\leq 1}(\Phi, B)$ on $\overline{V}$ given by~\eqref{T_1} and~\eqref{T_leq0} is well-defined. On the other hand, the group $\St^{\leq 1}(\Phi, B)$ is isomorphic to $\St(\Phi, B)$ by~\cref{lemma33} which implies the first assertion.

@@

\begin{lemma}
For $g_1 \in \overline{G}_M^{\geq 0}$ and $v\in \overline{V}$ one has $\overline{p}(t(g_1) \cdot v) = g_1 \cdot \overline{p}(v)$, where $t$ is the map from~\cref{lem:lemma32}.
\end{lemma}
\begin{proof} 
It suffices to verify the assertion for the generators $g = z_\alpha(f, \xi)$ of the subgroup $\overline{G}^{\geq 0}_M$ for all $f \in M[X]$, $\xi\in A[X]$. We accomplished this by induction on the degree of $\xi$ in $X$.
It is obvious, that the assertion holds in the case $\xi = a \in A$.

>>>>

@@

\item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
\item If $\alpha+\beta\in\Phi$, then holds:
\begin{multline} \label{Z5} z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s)\cdot x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
  x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta)\text{ where $\epsilon = N_{\alpha,\beta}$.}\end{multline}
\end{enumerate} \end{lemma}
\begin{proof}
The first four assertions are contained in~\cite[Lemma~9]{S15}, so it remains to verify the last assertion.
Direct computation shows that
\begin{multline} \nonumber
  z_{\alpha+\beta}(s\eta, \xi) = [x_\alpha(\epsilon s)^{x_{-\alpha-\beta}(\xi)}, x_\beta(\eta)^{x_{-\alpha-\beta}(\xi)}] =
  [x_\alpha(\epsilon s) x_{-\beta}(-s\xi), x_{\beta}(\eta) x_{-\alpha}(\epsilon \xi\eta)] = \\ 
  = x_\alpha(\epsilon s) \cdot x_{-\beta}(-s\xi) \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta)^{x_{\beta}(-\eta)} \cdot z_{-\beta}(s\xi, -\eta)^{x_{-\alpha}(-\epsilon \xi\eta)},
\end{multline} 
and the required assertion follows from~\eqref{Z2}.
\end{proof}

@@

Finally, the final relation can be verified by the following direct computation, which involves identity $[x, yz]^y = [y^{-1}, x] \cdot [x, z]$ and \eqref{HW-variant} with both sides of the equation inverted:
\begin{multline} \nonumber [x_{\alpha+\beta}(s), x_{-\alpha-\beta}(t\xi)] = [x_{\alpha+\beta}(s), [x_{-\alpha}(-\epsilon t), x_{-\beta}(\xi)]] = \\ 
= \left([[ x_{\alpha+\beta}(-s), x_{-\alpha}(\epsilon t)], x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s)} \cdot  [[ x_{-\beta}(-\xi), x_{\alpha+\beta}(s)], x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)}\right)^{x_{-\alpha}(\epsilon t)} = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t)] ^ {x_{-\beta}(-\xi)x_{-\alpha}(\epsilon t)}  = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [ x_{\alpha}(\epsilon s\xi), x_{-\alpha}(\epsilon t) x_{-\alpha-\beta}(t\xi)] ^ {x_{-\alpha}(\epsilon t)} = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot  [x_{-\alpha}(-\epsilon t), x_{\alpha}(\epsilon s\xi)] \cdot [x_{\alpha}(\epsilon s\xi), x_{-\alpha-\beta}(t\xi)] = \\
= [x_{\beta}(st), x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2). \qedhere
\end{multline}
\end{proof}

@@

\section{Proof of the second part of the injectivity theorem}
\subsection{Presentation of Steinberg groups by homogeneous generators}
\label{sec:presentation}
Let $M\trianglelefteq A$ be an ideal of a commutative ring $A$.
We consider $A[t, t\inv]$ as a $\mathbb{Z}$-graded ring in which $t$ has degree $1$.
We denote by $B = B(A, M)$ the subring $A[t] + M[t\inv] \subseteq A[t, t\inv]$ with the induced grading.
As an $A$-module $B$ decomposes as $\oplus_{d\in\mathbb Z}B_d$ where $B_d=M \cdot t^d$ for $d<0$, and $B_d=A \cdot t^d$ for $d\geq0$. Obviously, $B = A[t]$ in the case $M=0$ and $B = A[t, t\inv]$ in the case $M=A$.

@@

Finally, suppose $g$ has type $5$.
Substituting in~\eqref{Z5} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$ and expressing $z_\alpha(f, mX)$ through other terms we obtain that
\begin{multline} \label{eq:zalpha} z_\alpha(f, mX) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-mX^2 f) \cdot x_{-\beta}(mf) \cdot x_\alpha(f) \cdot \\ 
 \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon m) \cdot z_{-\beta}(-mf, -X) \cdot x_{-\alpha-\beta}(-\epsilon m^2X f) \cdot x_{-\alpha}(-m^2X^2 f), \end{multline}
and the latter expression is a product of generators of type 1, 1, 2, 5, 1, 2, 1, 4. \end{proof}

@@

Let us verify the assertion for the generator of type 4.
Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$. 
Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \beta$ into~\eqref{Z5} we obtain that
\begin{multline} \label{eq:Zconj3} z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
 \cdot z_{-\alpha-\beta}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\beta}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{-\beta}(a f, -X), \end{multline}
where $\epsilon = N_{-\alpha-\beta,\beta}$. 
Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 4, 1, 1, 5, 2. \end{proof}

@@

\subsection{Construction of a model for $\St(\Phi, A[X\inv] + M[X])$}
Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise. Let $A$ be a local ring with maximal ideal $M$. As in~\cref{firstPart} we denote by $B$ the ring $A[X\inv] + M[X]$ considered as a graded subring of the ring of Laurent polynomials $R = A[X, X\inv]$.

For shortness we denote the subgroup $\overline{\St}(\Phi, A, M)$ by $G_M^0$.
Notice that $G_M^0$ can be considered as a subgroup of $\St(\Phi, R)$.
\[ \xymatrix{ G_M^0 \ar@{^{(}->}[r]^{i_+} \ar@{^{(}->}[d]^{i_-} & \overline{\St}(\Phi, A[X], M[X]) \ar^{j_+^M}[d] \ar@{^{(}->}[r] & \St(\Phi, A[X]) \ar[dl]^{j_+} \\
              \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, R) &  } \] 
We denote by $\overline{G}^{\geq 0}_M$ the image of the map $j_+^M$. 
Denote by $V$ the subset of \[\St(\Phi, R) \times \St(\Phi, A[X\inv]) \times (1 + M)^\times\] consisting of those triples $(g, h, u)$ for which
\[p(g, h, u) := g \cdot j_-(h) \cdot \{ X, u \}\] belongs to $\overline{G}_M^{\geq 0}$.

@@

 Next, let us show that the value of $T_\alpha(aX^{-1})$ does not depend on a choice of the representative.
 Let $(g, h_1, u) \sim (g, h_2, u)$ be elements of the same orbit for which both $p(g, h_1, u)$ and $p(g, h_2, u)$ belong to $P_\alpha(*)$.
 By definition, $h_1^{-1} h_2 = i_-(h_0)$, for some $h_0 \in G^0_M$, moreover, 
  $p(g, h_1, u)^{-1} \cdot p(g, h_2, u) = j_- i_-(h_0) = j_+ i_+(h_0) \in P_\alpha(*)$.
 By~\cref{Pstar-char} there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $g_0 := ev^*_{X=0}(g_1) \in Z_\alpha(A, M)$ and $j_+(g_1) = j_+ i_+ (h_0)$.
 From the last equality and the injectivity of the map $G(\Phi, A[X]) \to G(\Phi, R)$ we obtain that the projections of $g_0$, $g_1$ and $h_0$ in $G(\Phi, R)$ are equal, which shows that $g_0 \cdot h_0^{-1} \in \overline{\K_2}(\Phi, A, M)$. It follows from Stein's theorem that the latter subgroup is generated by relative Steinberg symbols $\{ a, 1 + m \}$ and therefore is contained in $Z_\alpha(A, M)$ by~\cref{Z-DS}. Thus, we have obtained that $h_0 \in Z_\alpha(A, M)$ and hence that $i_-(h_0)$ is centralized by $X_\alpha(A[X^{-1}])$, which allows us to conclude that
 \begin{multline} \nonumber
  t_\alpha(aX^{-1})(g, h_1, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) \sim \\
  \sim \left( x_\alpha(aX^{-1})\cdot g ,\ h_1 i_-(h_0) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right) = t_\alpha(aX^{-1})(g, h_2, u). \qedhere
 \end{multline} \end{proof}

@@

@@

\begin{lemma} \label{R2_0_1} The operators $T_\alpha(aX^{-1})$ satisfy Steinberg relations $\mathrm{R2}_{0,1}$. \end{lemma}
\begin{proof} 
Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$.
As before, we may assume $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m, m' \in M$.
Now for $a, b \in A$ set $\epsilon = N_{\alpha, \beta},$ $c = 1 - \epsilon abm'$.
Applying~\cref{SR:obtuse} to the pair of roots $\alpha, \alpha+\beta$ we obtain that 
\begin{multline} \nonumber
[T_\beta(b), T_\alpha(aX^{-1})] \left(g, [h], u \right) = \\
 %= T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1}) \cdot g, \left[h \cdot x_\alpha\left(\tfrac{aX^{-1}}{1-am}\right)\right], u (1 - am) \right) = \\
 = T_\beta(b) \cdot T_\alpha(aX^{-1}) \left(x_\beta(-b) \cdot x_\alpha (-a X^{-1}) g,\ [h'],\ u (1 - am) \right) = \\
 = \left([x_\beta(b), x_\alpha(aX^{-1})]\cdot g,\ [h''],\ u c\right) = T_{\alpha+\beta}(-\epsilon abX^{-1})(g,\ [h],\ u),\end{multline} 
 where $h' = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \cdot x_{\beta}(bc)$  
  and the last equality is obtained as follows:
 \begin{multline} \nonumber
 h'' = h' \cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) \sim \\ \sim  h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1})\cdot x_{\alpha + \beta}\left(\epsilon ab(1-am)X^{-1}\right)\cdot x_\alpha\left(-\tfrac{a(1 - am)X^{-1}}{c}\right) = \\
 = h\cdot x_\alpha\left(\tfrac{a X^{-1}}{1-am}\right) \cdot x_{\alpha + \beta}\left(\tfrac{\epsilon \cdot abX^{-1}}{c}\right)\cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 - am}\right) \cdot h_{\alpha}^{-1}(1-am)\cdot h_{\beta}(c^{-1}) \sim
 h\cdot x_{\alpha + \beta}\left(\tfrac{\epsilon   abX^{-1}}{1 - \epsilon a b m'}\right). \qedhere
\end{multline}
\end{proof}

@@

This action satisfies the following additional property. If $v = (g, [h], u) \in \overline{V}$ is such that $\overline{p}(v) = \overline{1} = G_M^0$ then for any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_-(h_1) \cdot v = (h_1 \cdot g, [h \cdot h_1^{-1}], u)$ and, moreover, $\overline{p}(j_-(h_1) \cdot v) = \overline{1}$.
\end{prop}
\begin{proof}
  By~\cref{superfluous-relations} and Lemmas~\ref{R3_leq0_1}--\ref{R2_0_1} the action of $\St^{\leq 1}(\Phi, B)$ on $\overline{V}$ given by~\eqref{T_1} and~\eqref{T_leq0} is well-defined. On the other hand, the group $\St^{\leq 1}(\Phi, B)$ is isomorphic to $\St(\Phi, B)$ by~\cref{lemma33} (set $t = X^{-1}$).

@@

Denote by $I$ the ideal $M[X, X\inv]$ of $B$ (and also of $R$).
We denote by $t$ the map $\St(\Phi, R, I) \to \St(\Phi, B)$ from~\cref{lem:lemma32}.
\begin{lemma} For $v\in \overline{V}$ and any $g \in \St(\Phi, R, I)$ holds $\overline{p}(t(g) \cdot v) = \mu_R(g) \cdot \overline{p}(v)$. \end{lemma}
\begin{proof} First of all, notice that the assertion of the lemma can be verified by direct computation using~\eqref{T_1} and~\eqref{T_leq0} in the cases $g = z_\alpha(f, a)$ or $g = z_\alpha(X^2f, aX^{-1})$ for all $a\in A$, $f\in M[X]$. Notice that in both cases $g$ is contained in the image of $\St(\Phi, B, I)$, therefore $t$ acts identically on it.

It suffices to verify the assertion of the lemma for the generators $g = z_\alpha(f, \xi)$ of $\St(\Phi, R, I)$ for all $f \in M[X]$, $\xi\in A[X]$, $\alpha \in \Phi$. We accomplish this by 
induction on the degree of $\xi$ in $X$. The base of induction is clear by the above observation.
